# proxysnps

`proxysnps` is an R package that implements functions to get proxy SNPs
in [linkage disequilibrium][LD] (LD) with a [SNP] in the [1000 Genomes
Project][1000genomes].

```{r libraries, echo=FALSE, results='hide', warning=FALSE, error=FALSE, message=FALSE, cache=FALSE}
library(knitr)
opts_chunk$set(
  cache = TRUE,
  autodep = TRUE,
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  cache.path = "cache/README/",
  fig.path = "figures/README/",
  concordance = TRUE
)
```

## Install

```{r install, eval=FALSE, echo=TRUE}
install.packages("devtools")
devtools::install_github("slowkow/proxysnps")
```

## Examples

### Get proxy SNPs

Get the `R.squared` and `D.prime` between our SNP of interest `rs11063140` at
position 583,090 ([GRCh37]) and all other SNPs within a 100 kilobase window:

```{r get_proxies, echo=TRUE}
library(proxysnps)
d <- get_proxies(chrom = "12", pos = 583090, window_size = 1e5, pop = "AFR")
kable(head(d))
```

### Plot the linkage disequilibirum (LD)

Plot the LD between our SNP and all others within a 100 kilobase window:
  
```{r plot_r2, echo=TRUE, fig.width=10}
library(ggplot2)
ggplot() +
  geom_point(data = d, aes(x = POS, y = R.squared), size = 2) +
  geom_text(
    data = d[d$CHOSEN,,drop=FALSE],
    aes(x = POS, y = R.squared, label = ID),
    hjust = -0.1, size = 4
  ) +
  theme_bw(base_size = 14) +
  labs(x = "Position", y = bquote("R"^2))
```

### Get data for a genomic region

Get data describing African individuals, metadata for each SNP, and
genotypes for each SNP and each individual:

```{r get_vcf, echo=TRUE}
vcf <- get_vcf(chrom = "12", start = 533090, end = 623090, pop = "AFR")
names(vcf)
```

```{r vcf_ind_table, echo=TRUE}
kable(vcf$ind[1:5,])
```

```{r vcf_meta_table, echo=TRUE}
kable(vcf$meta[10:15,])
```

```{r vcf_geno_table, echo=TRUE}
kable(vcf$geno[10:15,1:5])
```

## Contributing

Please [submit an issue][issues] to report bugs or ask questions.

Please contribute bug fixes or new features with a [pull request][pull] to this
repository.

[issues]: https://github.com/slowkow/proxysnps/issues
[pull]: https://help.github.com/articles/using-pull-requests/

## Related work

[HaploReg][haploreg]

> HaploReg is a tool for exploring annotations of the noncoding genome at
> variants on haplotype blocks, such as candidate regulatory SNPs at
> disease-associated loci. Using [LD] information from the [1000 Genomes
> Project][1000genomes], linked SNPs and small indels can be visualized along
> with chromatin state and protein binding annotation from the [Roadmap
> Epigenomics][roadmap] and [ENCODE] projects, sequence conservation across
> mammals, the effect of SNPs on regulatory motifs, and the effect of SNPs on
> expression from [eQTL] studies.

[LocusZoom][locuszoom]

> LocusZoom is a tool to plot regional association results from genome-wide
> association scans or candidate gene studies.

[SNAP][snap] (defunct)

> SNAP is a computer program and web-based service for the rapid retrieval of
> linkage disequilibrium proxy SNP results given input of one or more query
> SNPs and based on empirical observations from the [International HapMap
> Project][hapmap] and the [1000 Genomes Project][1000genomes].

[Tagger][tagger]

> Tagger is a tool for the selection and evaluation of tag SNPs from genotype
> data such as that from the [International HapMap Project][hapmap]. It
> combines the simplicity of pairwise tagging methods with the efficiency
> benefits of multimarker haplotype approaches.

[LD]: https://en.wikipedia.org/wiki/Linkage_disequilibrium
[SNP]: https://en.wikipedia.org/wiki/Single-nucleotide_polymorphism
[eQTL]: https://en.wikipedia.org/wiki/Expression_quantitative_trait_loci

[hapmap]: http://www.hapmap.org/
[1000genomes]: http://www.1000genomes.org/
[GRCh37]: http://www.1000genomes.org/faq/which-reference-assembly-do-you-use
[roadmap]: http://www.roadmapepigenomics.org/
[ENCODE]: https://www.encodeproject.org/

[haploreg]: http://www.broadinstitute.org/mammals/haploreg/
[locuszoom]: http://locuszoom.sph.umich.edu/locuszoom/
[snap]: http://www.broadinstitute.org/mpg/snap/
[tagger]: https://www.broadinstitute.org/mpg/tagger/
