```{r libraries, echo=FALSE, results='hide', warning=FALSE, error=FALSE, message=FALSE, cache=FALSE}
library(knitr)
opts_chunk$set(
  cache = TRUE,
  autodep = TRUE,
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  cache.path = "cache/proxysnps/",
  fig.path = "figures/proxysnps/",
  concordance = TRUE
)
```

## Get proxy SNPs

Get the `R.squared` and `D.prime` between our [SNP] of interest `rs11063140` at
position 583,090 ([GRCh37]) and all other SNPs from phase 3 of the [1000
Genomes Project][1000genomes] within a 100 kilobase window:

```{r get_proxies, echo=TRUE}
library(proxysnps)
d <- get_proxies(chrom = "12", pos = 583090, window_size = 1e5, pop = "AFR")
kable(head(d))
```

## Plot the linkage disequilibirum (LD)

Plot the [LD] between our SNP and all others within a 100 kilobase window:
  
```{r plot_r2, echo=TRUE, fig.width=12, fig.height=4}
library(ggplot2)
ggplot() +
  geom_point(data = d, aes(x = POS, y = R.squared), size = 2) +
  geom_text(
    data = d[d$CHOSEN,,drop=FALSE],
    aes(x = POS, y = R.squared, label = ID),
    hjust = -0.1, size = 6
  ) +
  theme_bw(base_size = 18) +
  labs(x = "Position", y = bquote("R"^2))
```

## Get data for a genomic region

Get data describing African individuals, metadata for each SNP, and
genotypes for each SNP and each individual:

```{r get_vcf, echo=TRUE}
vcf <- get_vcf(chrom = "12", start = 533090, end = 623090, pop = "AFR")
names(vcf)
```

```{r vcf_ind_table, echo=TRUE}
kable(vcf$ind[1:5,])
```

```{r vcf_meta_table, echo=TRUE}
kable(vcf$meta[10:15,])
```

```{r vcf_geno_table, echo=TRUE}
kable(vcf$geno[10:15,1:5])
```

[LD]: https://en.wikipedia.org/wiki/Linkage_disequilibrium
[SNP]: https://en.wikipedia.org/wiki/Single-nucleotide_polymorphism

[1000genomes]: http://www.1000genomes.org/
[GRCh37]: http://www.1000genomes.org/faq/which-reference-assembly-do-you-use
